Run aquaculture model for Atlantic salmon

### 2025-07-25 06_run_atlantic_salmon_model.qmd
Runs

Note that this takes a long time - each branch of farmrun takes ~5 minutes, and a maximum of ~12 workers can run at a time. The total therefore takes ~17 hours.

@@

targets::tar_make(seconds_meta_append = 90)

@@

targets::tar_load(stat_names)
targets::tar_load(farm_results)
targets::tar_load(cohort_results)

purrr::map(stat_names, function(stat_name) {
  farm_results %>% 
    filter(measure == stat_name) %>% 
    qsave(file.path(output_model_farm_path, str_c(stat_name, "_all_farms.qs")))

  cohort_results %>% 
    filter(measure == stat_name) %>% 
    qsave(file.path(output_model_cohort_path, str_c(stat_name, "_all_farms.qs")))
})

@@

purrr::map(stat_names, function(stat_name) {
  farm_fnms %>% 
    str_subset(stat_name) %>% 
    qs::qread() %>% 
    merge(farm_bioms, by = c("farm_ID", "feed", "t")) %>% 
    rename(
      mean = mean.x,
      sd = sd.x,
      biom_mean = mean.y,
      biom_sd = sd.y
    ) %>% 
    mutate(
      biom_sd_mean = biom_sd/biom_mean,
      mean_perbiom = mean/biom_mean,
      sd_perbiom = (sd_mean+biom_sd_mean) * mean_perbiom
    ) %>% 
      qs::qsave(file.path(per_biomass_farm_path, str_c(stat_name, "_all_farms.qs")))

  cohort_fnms %>% 
    str_subset(stat_name) %>% 
    qs::qread() %>% 
    merge(cohort_bioms, by = c("farm_ID", "feed", "t")) %>% 
    rename(
      mean = mean.x,
      sd = sd.x,
      biom_mean = mean.y,
      biom_sd = sd.y
    ) %>% 
    mutate(
      biom_sd_mean = biom_sd/biom_mean,
      mean_perbiom = mean/biom_mean,
      sd_perbiom = (sd_mean+biom_sd_mean) * mean_perbiom
    ) %>% 
      qs::qsave(file.path(per_biomass_cohort_path, str_c(stat_name, "_all_farms.qs")))
})
```

>>>>

Note that this takes a long time - each branch of farmrun takes ~5.3 minutes, and a maximum of ~12 workers can run at a time. The total therefore takes ~17 hours.

@@

targets::tar_make(
  names = c("farm_run", "farm_results", "cohort_results"),
  seconds_meta_append = 90
)

@@

targets::tar_load(stat_names)
targets::tar_load(farm_IDs)
targets::tar_load(feed_names)
branches <- length(stat_names) * length(farm_IDs) * length(feed_names)
branches <- split(1:branches, ceiling(1:branches/length(farm_IDs)))

for (stat_name in stat_names) {
  farm_results <- purrr::map(branches, function(br) {
    targets::tar_load(farm_results, branches = br)
    farm_results %>% 
      filter(measure == stat_name)
  })
  farm_results <- bind_rows(farm_results)
  qsave(farm_results, file.path(output_model_farm_path, str_c(stat_name, "_all_farms.qs")))

  cohort_results <- purrr::map(branches, function(br) {
    targets::tar_load(cohort_results, branches = br)
    cohort_results %>% 
      filter(measure == stat_name)
  })
  cohort_results <- bind_rows(cohort_results)
  qsave(cohort_results, file.path(output_model_cohort_path, str_c(stat_name, "_all_farms.qs")))

  print(str_c("Files saved for ", stat_name))
}

@@

purrr::map(stat_names, function(stat_name) {
  farm_fnms %>% 
    str_subset(stat_name) %>% 
    qs::qread() %>% 
    merge(farm_bioms, by = c("farm_ID", "feed", "t")) %>% 
    rename(
      mean = mean.x,
      sd = sd.x,
      biom_mean = mean.y,
      biom_sd = sd.y
    ) %>% 
    mutate(
      biom_sd_mean = biom_sd/biom_mean,
      mean_perbiom = mean/biom_mean,
      sd_perbiom = (sd/mean+biom_sd_mean) * mean_perbiom
    ) %>%
      qs::qsave(file.path(per_biomass_farm_path, str_c(stat_name, "_all_farms.qs")))

  cohort_fnms %>% 
    str_subset(stat_name) %>% 
    qs::qread() %>% 
    merge(cohort_bioms, by = c("farm_ID", "feed", "t")) %>% 
    rename(
      mean = mean.x,
      sd = sd.x,
      biom_mean = mean.y,
      biom_sd = sd.y
    ) %>% 
    mutate(
      biom_sd_mean = biom_sd/biom_mean,
      mean_perbiom = mean/biom_mean,
      sd_perbiom = (sd/mean+biom_sd_mean) * mean_perbiom
    ) %>%
      qs::qsave(file.path(per_biomass_cohort_path, str_c(stat_name, "_all_farms.qs")))
})
```
